Stateless Model Checking with Data-Race Preemption Points

### 2016-08-09 oopsla-16/evaluation.tex
update timeouts/subsets

\begin{table*}[t]
	\begin{center}
		\small
		\revisionx{
	\begin{tabular}{r|c||c|c|c|c|c||c|c||c|c}
		& {\bf Num.} & {\bf QS-LHB} & {\bf QS-PHB} & {\bf ICB} & {\bf DPOR} & {\bf ShMem} & {\bf LHB DR} & {\bf Nondet.} & {\bf Mutual} & {\bf Avg. tested} \\
		{\bf Test} & {\bf tested} & {\bf bugs} & {\bf bugs} & {\bf bugs} & {\bf bugs} & {\bf bugs} & {\bf bugs} & {\bf DR bugs} & {\bf timeouts} & {\bf subset SSes} \\
		\hline
				% XXX FIXME: Need rerun nondet dr expt!
				% #test  qs-lhb  qs-phb   icb     dpor    everyw  dronly  nondets timeout comp.SSes
		{\tt bcast}	& 79	& 8	& 8	& 5	& 6	& 7	& 2	& 4	& 7	& 112.3	\\
		{\tt join} 	& 79	& 23	& 20	& 13	& 13 	& 14	& 11	& 6	& 11	& 75.9	\\
		{\tt mx} 	& 79	& 10	& 9	& 1	& 1	& 12	& 9	& 1	& 0	& -	\\
		{\tt sem} 	& 79	& 17	& 16	& 12	& 11	& 12	& 7	& 5	& 36	& 93.4	\\
		{\tt signal} 	& 79	& 10	& 8	& 5	& 5	& 11	& 6	& 6	& 45	& 59.0	\\
		{\tt rwlock} 	& 79	& 27	& 26	& 25	& 23	& 28	& 4	& 2	& 43	& 88.3	\\
		\hline
		{\tt sched} 	& 59	& 7	& 7	& 1	& 1	& 8	& 6	& 4	& 2	& 13.0	\\
		{\tt alarm} 	& 44	& 21	& 12	& 16	& 5	& 29	& 17	& 3	& 16	& 8.1	\\
		{\tt wait} 	& 52	& 30	& 27	& \revisionz{24}
								& 23	& 1	& 7	& 1	& 13	& 32.8	\\
		\hline
		{\bf Total}	& 629	& 153	& 133	& \revisionz{102}
								& 88	& 122	& 69	& 32	& 173	& 69.5 	\\
	\end{tabular}
		}
	\end{center}
	\caption{Summary of bugs
	%and data races
	found by each test program.
		\revisionx{QS-LHB and QS-PHB are \quicksand; ICB/DPOR/ShMem are the controls (\sect{\ref{sec:eval-setup}}).}
		``LHB DR bugs'' counts among \revisionx{QS-Limited-HB's} bugs how many required data-race PPs to expose (\sect{\ref{sec:eval-sssmc}});
	among those, ``Nondeterministic DR bugs'' counts how many candidates required MC integration to identify (\sect{\ref{sec:eval-dr}}).
	``Mutual timeouts'' counts how often both \revisionx{QS-Limited-HB and SSS-MC-ICB} timed out with no bug found;
	among those, ``Average tested subset SSes'' counts how many partial verifications \quicksand~provided on average for each test (\sect{\ref{sec:eval-sssmc}}).
		}
	\label{tab:drbugs}
\end{table*}

>>>>

\begin{table*}[t]
	\begin{center}
		\small
		\revisionx{
	\begin{tabular}{r|c||c|c|c|c|c||c|c||c|c}
		& {\bf Num.} & {\bf QS-LHB} & {\bf QS-PHB} & {\bf ICB} & {\bf DPOR} & {\bf ShMem} & {\bf LHB DR} & {\bf Nondet.} & {\bf Mutual} & {\bf Avg. tested} \\
		{\bf Test} & {\bf tested} & {\bf bugs} & {\bf bugs} & {\bf bugs} & {\bf bugs} & {\bf bugs} & {\bf bugs} & {\bf DR bugs} & {\bf timeouts} & {\bf subset SSes} \\
		\hline
				% XXX FIXME: Need rerun nondet dr expt!
				% #test  qs-lhb  qs-phb   icb     dpor    everyw  dronly  nondets timeout comp.SSes
		{\tt bcast}	& 79	& 8	& 8	& 5	& 6	& 7	& 2	& 4	& 7	& 112.3	\\
		{\tt join} 	& 79	& 23	& 20	& 13	& 13 	& 14	& 11	& 6	& \revisionz{12}
													& \revisionz{69.7}	\\
		{\tt mx} 	& 79	& 10	& 9	& 1	& 1	& 12	& 9	& 1	& 0	& -	\\
		{\tt sem} 	& 79	& 17	& 16	& 12	& 11	& 12	& 7	& 5	& \revisionz{50}
													& \revisionz{77.4}	\\
		{\tt signal} 	& 79	& 10	& 8	& 5	& 5	& 11	& 6	& 6	& 45	& \revisionz{59.6}	\\
		{\tt rwlock} 	& 79	& 27	& 26	& 25	& 23	& 28	& 4	& 2	& \revisionz{44}
													& \revisionz{86.3}	\\
		\hline
		{\tt sched} 	& 59	& 7	& 7	& 1	& 1	& 8	& 6	& 4	& 2	& 13.0	\\
		{\tt alarm} 	& 44	& 21	& 12	& 16	& 5	& 29	& 17	& 3	& \revisionz{17}
													& \revisionz{7.8}	\\
		{\tt wait} 	& 52	& 30	& 27	& \revisionz{24}
								& 23	& 1	& 7	& 1	& \revisionz{15}
													& \revisionz{33.8}	\\
		\hline
		{\bf Total}	& 629	& 153	& 133	& \revisionz{102}
								& 88	& 122	& 69	& 32	& \revisionz{192}
													& \revisionz{65.8} 	\\
	\end{tabular}
		}
	\end{center}
	\caption{Summary of bugs
	%and data races
	found by each test program.
		\revisionx{QS-LHB and QS-PHB are \quicksand; ICB/DPOR/ShMem are the controls (\sect{\ref{sec:eval-setup}}).}
		``LHB DR bugs'' counts among \revisionx{QS-Limited-HB's} bugs how many required data-race PPs to expose (\sect{\ref{sec:eval-sssmc}});
	among those, ``Nondeterministic DR bugs'' counts how many candidates required MC integration to identify (\sect{\ref{sec:eval-dr}}).
	``Mutual timeouts'' counts how often both \revisionx{QS-Limited-HB and SSS-MC-ICB} timed out with no bug found;
	among those, ``Average tested subset SSes'' counts how many partial verifications \quicksand~provided on average for each test (\sect{\ref{sec:eval-sssmc}}).
		}
	\label{tab:drbugs}
\end{table*}
